### 2015-06-10 doc/notebook/2015-02-26_Bacterial_data_acquisition.Rmd
Fix variable name to match genome and gene number

#need actual category from LSU group
spread_sheet$category <- NA

metadata_genome_id <- gsub(".* (P?SCGC \\S*)", "\\1", spread_sheet$full_name)
metadata_genome_id["SCGC AAA003-L8"] <- "SCGC AAA003-L08"

@@

#these sequences are missing from metadata file
#metadata_genome_id[! metadata_genome_id %in% names(seq_numbers)]
#probably not a horrible thing since not all genomes could give a 16S rRNA gene
#sequence

@@

spread_sheet_good <- spread_sheet[-which(rownames(spread_sheet) %in% bad_accnos),]

>>>>

metadata_genome_id <- gsub(".* (P?SCGC \\S*)", "\\1", spread_sheet$full_name)
metadata_genome_id[metadata_genome_id=="SCGC AAA003-L8"] <- "SCGC AAA003-L08"

@@

#these sequences are missing from fasta file
#metadata_genome_id[! metadata_genome_id %in% names(seq_numbers)]
#probably not a horrible thing since not all genomes could give a 16S rRNA gene
#sequence

@@

spread_sheet_good <- full_spread_sheet[-which(rownames(full_spread_sheet) %in% bad_accnos),]
